### 2017-10-26 paper/sexSelectionSpacing-ver1.tex
Edit no education duration discussion

>>>>

Table \ref{tab:median_sex_ratio_low} shows the predictions for women 
with no education.
Overall, spacing is shorter the fewer boys a couple has, but the
differences in median duration are never more than 3 months and most
are only one or two months
(the exceptions to this pattern are mostly for small cells).
Furthermore, although the median duration generally increases over 
time---with the exception of the first spell---there is little 
change in the relative pattern of durations across sex compositions
over time.
These results point to an absence of sex-selective abortions for 
this group of women, which is also supported by the fact that
most of the predicted sex ratios are close to the natural sex ratio.%
\footnote{
I return to whether there are statistically significant 
differences below when examining sex ratios within spells.
}
